Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-10-06 ms.tex
equation for L_synch added

\subsection{Minimum gamma-ray flux}
\label{sec:Fmin}
For clusters that host radio halos we can derive a minimum gamma-ray flux in the hadronic
model of radio halos -- where the radio-emitting electrons are secondaries from CR interactions. 
Hadronic interactions channel about the same power into secondary electrons and $\pi^{0}$-decay
gamma rays. A stationary distribution of CR electrons loses all its energy to
synchrotron radiation for strong magnetic fields ($B \gg B_{\rmn{CMB}} \simeq 3.2 \mu$G), and thus the
ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and
thermal gas \citep{article:Voelk:1989, article:Pohl:1994, article:Pfrommer:2008}, in particular with
$\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.  Hence we can derive a minimum
gamma-ray flux in the hadronic model
\begin{equation}
\label{eq:Fmin}
F_{\gamma,\rmn{min}} = \frac{\dps A_{\gamma}}{\dps A_{\nu}}\frac{\dps L_{\nu}}{\dps 4\pi D_{\rmn{lum}}^{2}},
\end{equation}
where $L_{\nu}$ is the observed luminosity of the radio mini-halo, $D_{\rmn{lum}}$ denotes the
luminosity distance to the respective cluster, $A_\gamma$ and $A_\nu$ are dimensional constants
that depend on the hadronic physics of the interaction \citep{article:Pfrommer:2008,
Pfrommer_etal:2008}. Lowering the magnetic field would require an increase in the energy density of
CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated
gamma-ray flux.

@@

\item
We then solve for $B_{0}$ while matching the observed synchrotron profile and fixing the profile
of $X_{\CR}(r)$ as determined through the previous two steps. Note
that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution
would be degenerate.

\item
Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
$B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as a
function of magnetic field strength. Hence we have to iterate through the previous steps until our
solution for the minimum magnetic field $B_{0}$ is converged.
\end{enumerate}

>>>>

\subsection{Minimum gamma-ray flux}
\label{sec:Fmin}

For clusters that host radio halos we can derive a minimum gamma-ray flux in the hadronic model of
radio halos -- where the radio-emitting electrons are secondaries from CR interactions.  Hadronic
interactions channel about the same power into secondary electrons and $\pi^{0}$-decay gamma rays. A
stationary distribution of CR electrons loses all its energy to synchrotron radiation for strong
magnetic fields ($B \gg B_\rmn{CMB} \simeq 3.2 \mu$G, where $B_\rmn{CMB}$ is the equivalent magnetic
field strength of the CMB so that $B_\rmn{CMB}^2/8\pi$ equals the CMB energy density). Thus the
ratio of gamma-ray to synchrotron flux becomes independent of the spatial distribution of CRs and
thermal gas \citep{article:Voelk:1989, article:Pohl:1994, article:Pfrommer:2008}, in particular with
$\alpha_{\nu}\simeq 1$ as the observed synchrotron spectral index.  Hence we can derive a minimum
gamma-ray flux in the hadronic model
\begin{equation}
\label{eq:Fmin}
F_{\gamma,\rmn{min}} = \frac{\dps A_{\gamma}}{\dps A_{\nu}}\frac{\dps L_{\nu}}{\dps 4\pi D_{\rmn{lum}}^{2}},
\end{equation}
where $L_{\nu}$ is the observed luminosity of the radio mini-halo, $D_{\rmn{lum}}$ denotes the
luminosity distance to the respective cluster, $A_\gamma$ and $A_\nu$ are dimensional constants
that depend on the hadronic physics of the interaction \citep{article:Pfrommer:2008,
Pfrommer_etal:2008}. Lowering the magnetic field would require an increase in the energy density of
CR electrons to reproduce the observed synchrotron luminosity and thus increase the associated
gamma-ray flux.

@@

\item
We then solve for $B_{0}$ while matching the observed synchrotron profile and fixing the profile
of $X_{\CR}(r)$ as determined through the previous two steps. Note
that for $B_{0} \gg B_{\rmn{CMB}}$ and a radio spectral index of $\alpha_{\nu}=1$, the solution
would be degenerate since the luminosity of the radio halo scales as
\begin{equation}
\label{eq:Lnu}
L_{\nu} \propto \int dV Q(E)\,\frac{B^{1+\alpha_\nu}}{B^2 + B_{\rmn{CMB}}^2} \to \int dV Q(E),
\end{equation}
where $Q(E)$ denotes the electron source function.

\item Inverse Compton cooling of CR electrons on CMB photons introduces a characteristic scale of
  $B_{\rmn{CMB}}\simeq 3.2\,\mu$G which imprints as a non-linearity on the synchrotron emissivity as
  a function of magnetic field strength (see Eqn.~(\ref{eq:Lnu})). Hence we have to iterate through
  the previous steps until our solution for the minimum magnetic field $B_{0}$ is converged.
\end{enumerate}
